\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0pt}
\newcommand{\uhref}[2]{\href{#1}{\underline{#2}}}
\usepackage{xcolor}
\definecolor{mygray}{rgb}{.2,.23,.25}%#333a3f
\AtBeginDocument{\color{mygray}}
\pagenumbering{gobble}
\usepackage{fontawesome5}






% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi


\begin{document}

\begin{center}
    {\LARGE \textbf{Sepehr Fazeli}}\\[0.95em]
    \faMapMarker\enspace94469 Deggendorf, Bayern, Germany \, | \, 
    \faEnvelope\enspace\uhref{mailto:sepehr.fazeli@web.de}{sepehr.fazeli@web.de} \, | \, \faMobile\enspace\uhref{tel:+4915753239701}{+4915753239701}\\[0.25em]
    \faLinkedin\enspace\uhref{https://linkedin.com/in/sepehr-fazeli}{linkedin.com/in/sepehr-fazeli} \, | \, \faGithub\enspace\uhref{https://github.com/sepehrfazeli}{github.com/sepehrfazeli} \, | \, \faGitlab\enspace\uhref{https://mygit.th-deg.de/sf07627}{mygit.th-deg.de/sf07627}
\end{center}
\vspace{-2em}


%--------------------%
%      SUMMARY       %
%--------------------%
\newcommand{\summaryline}{-1.9em} 
\section*{Summary}
\vspace{-0.8em}
\hline
\vspace{0.2em}
Frontend Engineer with 4+ years’ experience building React-based enterprise applications, managing databases, and automating CI/CD pipelines in cloud environments. 
\vspace{-1.5em}

%--------------------%
%      SKILLS        %
%--------------------%
\newcommand{\skillspacing}{0.1em}
\section*{Skills}
\vspace{-0.8em}
\hline
\vspace{0.2em}
\begin{tabularx}{0.2\linewidth}{ l l }
\textbf{Frontend:} & React · Next.js(SSR/CSR) · TypeScript · JavaScript · SASS · WebGL/Three.js \\[\skillspacing]
\textbf{Backend:} & Node.js · C\# (.NET) · REST · GraphQL · RabbitMQ \\[\skillspacing]
\textbf{Databases \& BI Analytics:} & PostgreSQL · MongoDB · Matomo event tracking \& dashboards \\[\skillspacing]
\textbf{DevOps \& Cloud:} & Docker · Kubernetes · GitLab CI/CD · Jenkins · AWS (EC2, S3) \\[\skillspacing]
\textbf{Agile \& Methodologies:} & Agile · Kanban · Jira · Confluence · TDD (Jest, RTL, Cypress) \\[\skillspacing]
\textbf{Tools \& Collaboration} & Git · Linux · Postman · UAT facilitation \& stakeholder presentations\\[0.5em]
\textbf{Languages} & English (professional) · German B1 (actively pursuing B2 certification)
\end{tabularx}
\vspace{-1em}


%--------------------%
%      EXPERIENCE     %
%--------------------%
\section*{Professional Experience}
\vspace{-0.8em}
\hline
\vspace{0.2em}

\textbf{Dassault Systèmes Deutschland GmbH} \hfill Munich, Germany | Oct 2023 -- Present \\
\\
Contributing concurrently to three parallel projects (3DEXCITE Create \& Show, Tetra Pak) within a cross-functional team across India and Germany, delivering both internal and external customer solutions in an Agile environment.
\begin{itemize}[leftmargin=*]
    \item \textit{Tetra Pak} - \textit{Frontend Engineer}
        \begin{itemize}[leftmargin=*]
            \item Developed 20+ features, including authentication, API integration, and modern design development using React, TypeScript, Redux, WebGL, Tailwind, and JWT, meeting customer needs, and delivering a high-quality application.
            \item Containerized the frontend as a microservice—writing Dockerfiles and Helm charts—and integrated it into our Jenkins-driven Kubernetes CI/CD pipeline.
            \item Implemented 18+ technical event schemas into non-technical dashboards using Matomo, improving data-driven decision-making for client-facing features.
            \item Presented in UAT sessions with Tetra Pak stakeholders to demo new features.
        \end{itemize}
    \item \textit{3DEXCITE Create \& Show} - \textit{Frontend Engineer}
        \begin{itemize}[leftmargin=*]
            \item Closed 15+ Jira issues, including component redesign, performance issues, and API architecture change integration, using React, TypeScript, SQL, Redux, MUI, Storybook, WebAssembly, and RabbitMQ.
            \item Led a customer-facing documentation development interactive application with Hugo, Hextra, and Tailwind, applying custom design and animations to improve usability and brand alignment.
        \end{itemize}
    \item \textit{3DEXCITE DELTAGEN} -  \textit{Master Thesis}
        \begin{itemize}[leftmargin=*]
            \item Led a benchmark study to find alternative C\# image processing libraries, achieving a 400\% speedup, 50\% lower memory usage, and €5K/year in licensing savings.
        \end{itemize}
    \item \textit{3DEXPERIENCE Apex Cloud} - \textit{Frontend Engineer}
        \begin{itemize}[leftmargin=*]
            \item Modernized the legacy code base with React, ThreeJS, React Query, and Storybook, upgraded/replaced 8+ libraries, improving maintainability.
            \item Deployed it on AWS EC2 instances hosted on a custom domain for demo purposes, gaining approval from 10+ stakeholders to resume development after a year of stagnation.
        \end{itemize}
\end{itemize}

\textbf{SUMM AI} \hfill Munich, Germany | Sep 2022 -- Nov 2022 \\
\textit{Frontend Developer} 
\begin{itemize}[leftmargin=*]
    \item Implemented a complete frontend app redesign in collaboration with a UI/UX designer using React, TypeScript, MUI, and Redux, enhancing the interface and improving user experience.
    \item Configured ESLint and Prettier to enforce consistent code formatting, reducing style-related errors and elevating code quality.
\end{itemize}

\textbf{Gport} \hfill Tehran, Iran | Jan 2021 -- Feb 2022  \\
\textit{Frontend Developer}
\begin{itemize}[leftmargin=*]
    \item Built a new frontend using React, TypeScript, Storybook, and MobX, integrating 10+ RESTful endpoints and enforcing 90\%+ test coverage (Jest, Testing Library) to ensure reliability.
    \item Documented components with Storybook, streamlining developer onboarding and reducing new component implementation time.
\end{itemize}
\vspace{-1em}


%--------------------%
%      EDUCATION      %
%--------------------%
\section*{Education}
\vspace{-0.8em}
\hline
\vspace{0.2em}

\textbf{M.Sc. in Computer Science} \hfill Mar 2023 -- Mar 2025 \\
Deggendorf Institute of Technology\\
\textit{Relevant Coursework: Cloud Computing and Virtualization · Data Analytics · Architecture and Systems Engineering}\\
\\
\textbf{B.Sc. in Electrical Engineering} \hfill Mar 2016 -- Mar 2019 \\
Semnan University\\
\vspace{-2em}

%----------------------------%
%  Professional Development  %
%----------------------------%
\section*{Professional Development}
\vspace{-0.8em}
\hline
\vspace{0.2em}
\textbf{AWS Educate Introduction to Cloud 101} | Amazon Web Services (AWS)\hfill Apr 2025\\
\textbf{Front-End Engineer Career Path} | Codecademy \hfill Jan 2021\\
\textbf{Learn Node.js} | Codecademy \hfill Jan 2021\\




\end{document}
